{{< var titll >}}

### 2024-10-26 presentation.qmd
abc

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
library(polynom)
modlat <- eqpar$meql
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
#ssr <- selreport(ManifoldDestiny::appsn)
#rsr <- selreport(ManifoldDestiny::apprn)
#round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))
```

@@

## {{< var sec2.un1 >}}
- We have identified three ways of counting
  - *Standard form* ( $x$, $y$, $\zeta$, $\alpha$, $\lambda$ )
  - *Hybrid form* ( $g$, $h$, $\alpha$, $\Gamma$, $\Omega$ )
  - *Opposition form* ( $n$, $m$, $\xi$, $\Omega$, $\lambda$ )
-  Each form can (throught its parametric tautologies) determine the 5 parameters that have been listed.
  -  We are free to *predetermine* **3** of them
  -  The remaining **2** must be *backsolved*, this based on information from the first three parameters.
  -  Selecting **3** parameters from a set of **5** implies **10** different combinations

@@

::: {.callout-note collapse="true"}
```{r}
kable(laws1[,c(5,6,7,8)], format = "markdown", escape = FALSE) # %>% kableExtra::kable_styling(font_size=8)

@@

::: {.callout-note collapse="true"}
```{r} 
kable(laws2, format = "markdown", escape = FALSE)

@@

## {{< var sec2.un4 >}}

@@

## {{< var sec2.un1 >}}

@@

# {{< var sec3.nmn >}}

>>>>

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
library(polynom)
modlat <- eqpar$meql
laws_df1 <- ManifoldDestiny::eqdef$meql
laws1 <- laws_df1 
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
ssr <- selreport(ManifoldDestiny::appsn)
rsr <- selreport(ManifoldDestiny::apprn)
round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))
```

@@

## {{< var sec2.2.1 >}}
- We have identified three ways of counting
  - *Standard form* ( $x$, $y$, $\zeta$, $\alpha$, $\lambda$ )
  - *Hybrid form* ( $g$, $h$, $\alpha$, $\Gamma$, $\Omega$ )
  - *Opposition form* ( $n$, $m$, $\xi$, $\Omega$, $\lambda$ )
-  Each form can (throught its parametric tautologies) determine the 5 parameters that have been listed.
  -  We are free to *predetermine* **3** of them
  -  The remaining **2** must be *backsolved*, this based on information from the first three parameters.
  -  Selecting **3** parameters from a set of **5** implies **10** different combinations

@@

::: {.callout-note collapse="true"}
```{r}
#kable(laws1[,c(5,6,7,8)], format = "markdown", escape = FALSE) # %>% kableExtra::kable_styling(font_size=8)
```
:::

@@

::: {.callout-note collapse="true"}
```{r} 
#kable(laws2, format = "markdown", escape = FALSE)

@@

## {{< var sec2.2.2 >}}

@@

## {{< var sec2.2.5 >}}

@@

# {{< var sec3.1 >}}
